Manuscript analyses

### 2024-01-18 cilta_cel/Manuscript analyses.Rmd
Fix MVA and UVA

## Survival analysis - KM by gr3_cytopenia_90d
```{r Survival analysis - KM by gr3_cytopenia_90d}
surv_dat <- fig_dat %>% 
  mutate(ORR_as_best_response = case_when(
    ORR_as_best_response == "ORR"         ~ "ORR",
    is.na(ORR_as_best_response)           ~ "never ORR"
  ))

@@

```{r glm}
mva_dat <- surv_dat %>% 
  filter(os_from_infusion_months > 3) %>% 
  mutate(ORR_as_best_response = case_when(
    ORR_as_best_response == "ORR"         ~ 1,
    ORR_as_best_response == "never ORR"   ~ 0
  ))

glm(ORR_as_best_response ~ gr3_cytopenia_90d,
    data = mva_dat,
    family = "binomial") %>%
  tbl_regression(exponentiate = TRUE, 
                 intercept = TRUE) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  modify_spanning_header(everything() ~ "**ORR_as_best_response**") %>%
  bold_p(t = .05) 
```

>>>>

## Survival analysis - KM by gr3_cytopenia_90d
```{r Survival analysis - KM by gr3_cytopenia_90d}
surv_dat <- fig_dat %>% 
  mutate(ORR_as_best_response = case_when(
    ORR_as_best_response == "ORR"         ~ "ORR",
    ORR_as_best_response == "SD/PD"       ~ "never ORR",
    # TRUE                                  ~ "never ORR"
  ))

@@

## UVA best ORR by gr3 cytopenia at day 90
I was unable to perform the analyses investigating severe cytopenias at D90 and best response because everyone with severe cytopenias had an event.
```{r glm}
mva_dat <- surv_dat %>% 
  # filter(os_from_infusion_months > 3) %>% 
  mutate(ORR_as_best_response = case_when(
    ORR_as_best_response == "ORR"         ~ 1,
    ORR_as_best_response == "never ORR"   ~ 0
  ))

# glm(ORR_as_best_response ~ gr3_cytopenia_90d,
#     data = mva_dat,
#     family = "binomial") %>%
#   tbl_regression(exponentiate = TRUE, 
#                  intercept = TRUE) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   modify_spanning_header(everything() ~ "**ORR_as_best_response**") %>%
#   bold_p(t = .05) 
```
